\textbf{{\Large {Recursive algorithms, branching coefficients affine algebras and applications}}}

### 2010-02-18 AffineLieAlgebras/InformalNotes/article.tex
Some work on semisimple algebras

$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|}{\left|\Theta_{\mathfrak{a}}\right|}$ --- the embedding index.

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$, which is drawn as the black vector at the Figure \ref{fig:B2_A1}.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the Figure \ref{fig:B2_A1} we have also shown the set of points $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous points and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these points and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous points in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

To find the branching coefficients we need to compute the anomalous points of $B_4$, select point lying in the main Weyl chamber of $\mathfrak{a}_{\bot}$ and compute the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.

@@

The set of the anomalous points $\omega(\mu+\rho)-\rho,\; \omega\in W$
consists of 384 points. We do not show it here.

We need to select those points $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
It means that scalar product of these points with all the roots from $\Delta^{+}_{\bot}$ is non-negative.

To compute dimensions of the corresponding
$\mathfrak{a}_{\bot}$-modules we need to project each selected point
onto the root space $\Delta^{+}_{\bot}$ and substract
$\rho_{\mathfrak{a}_{\bot}}$, then use Weyl dimension formula.

We show the result of this procedure on the Figure \ref{fig:B4B2anom}.
\begin{figure}[h!tb]
    \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
  \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
\begin{figure}[h!tb]
  \includegraphics[width=130mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

The set of the anomalous points of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.

\begin{figure}[h!tb]
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the Figure
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.

@@

\subsection{Example}
\label{sec:example}

@@

The set of the anomalous points of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}. We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration. (Where, how? What are the coordinates, it is very difficult to see anything even in the zero grade!)

\begin{figure}[h!tb]
  \includegraphics[width=160mm]{AffineA2_A1_anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{A_2}$}
  \label{fig:affine_A2_anom_point}
\end{figure}

According to our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules (there are no such subalgebra here!)$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of these caculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

@@

>>>>

$x_e=\frac{\left|\pi_{\mathfrak{a}} \Theta\right|^2}{\left|\Theta_{\mathfrak{a}}\right|^2}$ --- the embedding index.

@@

Let's describe the reduction of fundamental representation of $B_2$ with the highest weight (in fundamental weight basis) equal to $(1,0)$, which is drawn as the black vector at the Figure \ref{fig:B2_A1}.
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1.pdf}
  }
  \caption{Regular embedding of $A_1$ into $B_2$}
  \label{fig:B2_A1}
\end{figure}
On the Figure \ref{fig:B2_A1} we have also shown the set of weights $\omega(\mu+\rho),\; \omega\in W$ of fundamental representation of $B_2$ with the corresponding determinants of Weyl reflections $\epsilon(\omega)$.
Now we have to factorise the Weyl group $W$ by $W_{\bot}=\left\{\omega_1\right\}$. We get the following set of anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W_{\bot}\backslash W$:
\begin{figure}[ph]
  \noindent\centering{
    \includegraphics[width=90mm]{B2_A1_2.pdf}
  }
  \caption{Anomalous weights and the corresponding $\mathfrak{a}_{\bot}=A_1$-modules}
  \label{fig:B2_A1_2}
\end{figure}
We have also depicted the corresponding $\mathfrak{a}_{\bot}=A_1$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
Then we project these weights and dimensions of modules onto the root space of subalgebra $\mathfrak{a}=A_1$ and get the following anomalous weights in fundamental weights basis with corresponding multiplicities:
\begin{equation}
  \label{eq:25}
  (1,2),\; (0,-3),\; (-4,3),\; (-5,-2)
\end{equation}
For the function $s(\gamma)$ and the set $\Gamma$ from the definition (\ref{phi-d},\ref{fan-defined}) we have
\begin{equation}
  \label{eq:22}
  (1,2),\; (2,-1)
\end{equation}
Here the second component denotes the value of $s(\gamma)$.

@@

To find the branching coefficients we need to compute the anomalous weights of $B_4$, select weights lying in the main Weyl chamber of $\mathfrak{a}_{\bot}$ and compute the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.

@@

The set of the anomalous weights $\omega(\mu+\rho)-\rho,\; \omega\in W$
consists of 384 elements. We do not show it here.

We need to select those weights $\omega(\mu+\rho)$  which are projected into the main chamber of the embedded algebra $\mathfrak{a}_{\bot}$.
It means that scalar product of these weights with all the roots from $\Delta^{+}_{\bot}$ is non-negative.

To compute dimensions of the corresponding
$\mathfrak{a}_{\bot}$-modules we need to project each selected weight
onto the root space $\Delta^{+}_{\bot}$ and substract
$\rho_{\mathfrak{a}_{\bot}}$, then use Weyl dimension formula.

We show the result of this procedure on the Figure \ref{fig:B4B2anom}.
\begin{figure}[h!tb]
    \includegraphics[width=150mm]{B4_B2_anom_points.pdf}
  \caption{Anomalous weights with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$, depicted at the Figure \ref{fig:B4B2Fan}.
\begin{figure}[h!tb]
  \includegraphics[width=130mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

The set of the anomalous weights of this representation up to sixth grade is depicted in the Figure \ref{fig:affine_B2_anom_point} and in each grade it looks like in the Figure \ref{fig:B2_A1}.

\begin{figure}[h!tb]
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous weights of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the Figure
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$: \ref{fig:AffineB2A1Fan}.
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2A1Fan}
\end{figure}

@@

Selecting the elements inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.

@@

For the maximal conformal embedding $\mathfrak{a}\subset\mathfrak{g}$ it is easy to see that $\mathfrak{a}_{\bot}$ is trivial, otherwise it would be non-maximal, since $\mathfrak{a}\subset\mathfrak{a}\oplus\mathfrak{a}_{\bot}\subset\mathfrak{g}$. We can get non-maximal conformal embeddings through the chain of maximal $\mathfrak{a}\subset\mathfrak{g}_1\subset\mathfrak{g}_2$. In this case the representations of $\mathfrak{g}_1,\mathfrak{g}_2$ have to be of level one, due to the equation \eqref{eq:111}. If we limit the consideration by the affine extensions of simple classical Lie algebras, the number of possible non-maximal conformal embeddings is rather small \cite{schellekens1986conformal}. We study the example of $\hat{A}_1\subset \hat{A}_2\subset\hat{A}_{?}$ in the section \ref{sec:non-maxim-conf}.

\subsection{Examples}
\label{sec:example}

@@

The set of the anomalous weights of this representation up to the sixth grade is depicted in the Figure \ref{fig:affine_A2_anom_point}. We also show the root subspace of the subalgebra $\hat{A}_1$ under consideration. (Where, how? What are the coordinates, it is very difficult to see anything even in the zero grade!)

\begin{figure}[h!tb]
  \includegraphics[width=160mm]{AffineA2_A1_anom.pdf}
  \caption{The anomalous weights of the $(1,0,1,0)$ representation of the algebra $\hat{A_2}$}
  \label{fig:affine_A2_anom_point}
\end{figure}

According to our algorithm \ref{sec:algorithm} we project the anomalous weights to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules (there are no such subalgebra here!)$L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of these caculations up to the twelfth grade is presented in the Figure \ref{fig:AffineA2_A1_anom_proj}
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineA2_A1_proj_anom.pdf}
  \caption{Projected anomalous weights and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineA2_A1_anom_proj}
\end{figure}

@@

\subsubsection{Embedding of semisimple subalgebras}
\label{sec:embedd-semis-subalg}

Embedding of affine extensions of semisimple subalgebras to affine lie algebras allows additional construction of modular invariants \cite{difrancesco1997cft}, \cite{walton1989conformal}. Consider the conformal embedding constructed as the affine extension  $\mathfrak{a}_{1}\oplus\mathfrak{a}_{2}\subset \mathfrak{g}$ of the embedding of semisimple subalgebra $\overset{\circ}{\mathfrak{a}}_1\oplus\overset{\circ}{\mathfrak{a}}_2$ into simple Lie algebra $\overset{\circ}{\mathfrak{g}}$.

Substituting the branching rules into \eqref{eq:34} we get non-diagonal mass matrix
\begin{equation}
  \label{eq:2}
  M_{\lambda\xi,\mu\eta}
\end{equation}
where $\lambda,\mu$ are the highest weights of the representations of $\mathfrak{a}_1$ and $\xi,\eta$ of $\mathfrak{a}_2$. A new $\mathfrak{a}_1$-invariant mass matrix can be found by the contraction of $M_{\lambda\xi,\mu\eta}$ with some known $\mathfrak{a}_2$-invariant mass matrix $M^{(2)}_{\xi\eta}$:
\begin{equation}
  \label{eq:35}
  M^{(1)}_{\lambda\mu}=\sum_{\xi,\eta\in P_{\mathfrak{a}}^{+}}M_{\lambda\xi,\mu\eta}M^{(2)}_{\xi\eta}
\end{equation}

Consider the embedding $\widehat{su(2)\oplus su(2)}\subset \hat{su(4)}$, which is the affine extension of the special embedding $su(2)\oplus su(2)\subset su(4)$. Let's construct the special embedding $su(2)\oplus su(2)\subset su(4)$ using the method of \cite{vasilevich1986method}. We start with 4-dimensional representation of $su(2)\oplus su(2)$ with the highest weight $(1,1)$.

, depicted at the Figure \ref{fig:a1a2a3}. This embedding is characterised by the embedding indexes $(2,2)$ and is conformal, since $c(A_1\oplus A_1)=c(A_1)+c(A_1)=2\frac{x_e \mathrm{dim}(A_1)}{x_e+2}=\frac{\mathrm{dim}A_3}{5}=c(A_3)$.

Four dominant weights of level one have the following coordinates in the orthogonal basis: 
\begin{equation}
  \begin{array}{lll}
     \omega_0 & = & (0,0,0,0;1;0)\\
     \omega_1 & = & (\frac{3}{4},-\frac{1}{4},-\frac{1}{4},-\frac{1}{4}; 1; 0)\\
     \omega_2 & = & (\frac{1}{2},\frac{1}{2},-\frac{1}{2},-\frac{1}{2}; 1; 0)\\
     \omega_3 & = & (\frac{1}{4},\frac{1}{4},\frac{1}{4},-\frac{3}{4}; 1; 0) \\
  \end{array}
\end{equation}
We limit our computation by the fifth grade.
The set of the anomalous weights of the representation of the algebra $\hat{A}_3$ consists of 192 elements.

\subsubsection{Non-maximal conformal embedding}
\label{sec:non-maxim-conf}

The example of the previous subsection \ref{sec:spec-embedd-hata_1s} has not demonstrated the features of our approach since the orthogonal subalgebra $\mathfrak{a}_{\bot}$ has been empty.

But we can consider the chain of embeddings $\mathfrak{a}\subset\mathfrak{g}_1\subset\mathfrak{g}_2$. We can use the embedding $\hat{A}_1\subset\hat{A}_2\subset\hat{A}_{?}$. Modular invariant partition function for this case could be obtained in two steps. First one can compute branching coefficients for $\hat{A}_2\subset\hat{A}_{?}$ and get partition function for $\hat{A}_2$ and then substitute the results of the previous section \ref{sec:spec-embedd-hata_1s} into it to get the new partition function for $\hat{A}_1$.

The algorithm of the section \ref{sec:algorithm} can be used to skip the intermediate computation.
